Individual Stellar Haloes of Massive Galaxies Measured to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-12-08 draft/paper1.tex
Final edits before resubmitt...again

% Version 0; preprint format; Written by SH
% Version 1; emulateapj format; Edited by SH and AL
% Version 2; emulateapj format; Edited by SH and AL
% Version 3; emulateapj format; Edited AL
% Version 4; emulateapj format; Edited SH
% Version 5; MNRAS format; Edited SH
% Version 6; MNRAS format; Paper I edited by JG
% Version 7; MNRAS format; Edited by SH

\documentclass[a4paper,fleqn,usenatbib]{mnras}

@@

\def\m2l{{$M_{\star}/L_{\star}$}}
\def\s2n{{$\mathrm{S}/\mathrm{N}$}}
\def\mden{{$\mu_{\star}$}}

% Commenting:
\newcommand{\xxx}[1]{\textcolor{red}{\textbf{XXX}}}
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
\newcommand{\addref}{{\textcolor{red}{REF}}}
\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
\newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
\newcommand{\jenny}[1]{\textcolor{Bittersweet}{\textbf{[Jenny: #1]}}}
\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
\newcommand{\update}[1]{\textcolor{PineGreen}{#1}}
%\newcommand{\update}[1]{#1}

@@

%% ------------------------------------------------------------------------------------ %% 
\title[Mass Dependent Stellar Halo in Massive Galaxies]{Tracing the Stellar Halo of 
	   Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam}

\author[S. Huang et al.]{
        Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
        Alexie Leauthaud,$^{2,1}$
        Jenny E. Greene,$^{4}$
        Kevin Bundy,$^{3,1}$
        \newauthor
        Yen-Ting Lin,$^{5}$
        Masayuki Tanaka,$^{5}$
        Rachel Mandelbaum,$^{7}$
        Satoshi Miyazaki,$^{5,8}$
        \newauthor
        Yutaka Komiyama,$^{5,8}$
        HSC collaboration 
        \\
        $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
              the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\
        $^{2}$Department of Astronomy and Astrophysics, University of California 
              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
        $^{3}$UCO/Lick Observatory, University of California, Santa Cruz,
              1156 High Street, Santa Cruz, CA 95064, USA\\
        $^{4}$Department of Astrophysical Sciences, Peyton Hall,
              Princeton University, Princeton, NJ 08540, USA \\
        $^{5}$National Astronomical Observatory of Japan, 2--21--1 Osawa, Mitaka, 
              Tokyo 181--8588, Japan\\
        $^{6}$Academia Sinica Institute of Astronomy and Astrophysics, 
              P.O. Box 23--141, Taipei 10617, Taiwan\\
        $^{7}$McWilliams Center for Cosmology, Department of Physics, 
              Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
        $^{8}$SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
              Tokyo, 181--8588, Japan
        }   
%% ------------------------------------------------------------------------------------ %% 
\date{Accepted XXX. Received YYY; in original form ZZZ}        
\pubyear{2017}

@@

    Massive galaxies are important to our understanding of galaxy formation, and 
    their extended stellar halos contain crucial fossil records of their assembly 
    history. 
    In this work, we use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), 
    high-quality (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) 
    survey to investigate the surface mass density profiles and outer stellar halos 
    of massive galaxies. 
    Our sample consists of ${\sim}7000$ massive (\mstar{}$\geq 11.5$) central galaxies 
    at $0.3 < z < 0.5$. 
    The depth of the HSC survey reaches ${\sim}4$ magnitudes fainter than SDSS and 
    enables us to directly trace stellar mass distributions to 100 kpc without 
    requiring stacking. 
    Shallow images and/or over-simplified models like the \texttt{CModel} tend to 
    miss the extended stellar halo and result in underestimated stellar mass in a 
    mass-dependent way.  
    It will impact important applications like the measurements of the stellar mass 
    function. 
    With these deeper data, we explicitly show that at fixed stellar mass,
    massive central galaxies display surface mass density profiles that are not 
    self-similar, with the outer-slope becoming shallower and the fraction of mass 
    in the outskirt increasing with total stellar mass.
    We also show that the ellipticity of the stellar halo increases with stellar
    mass, while the optical color gradients do not strongly depend on stellar mass.
    Our results are broadly consistent with the two phase formation scenario of 
    massive galaxies in which outer envelopes are built up at late times from the 
    accretions of small systems. 
    The surface mass density profiles are provided in a convenient tabulated format 
    in order to facilitate comparisons with predictions from numerical simulations 
    of galaxy formation.

@@

    Massive galaxies are fascinating objects that have experienced complex assembly 
    process and dramatic evolution.  
    They are crucial for both cosmology and the study of galaxy formation. 
    Simulations of structure formation within the context of the $\Lambda$-CDM 
    cosmological model make predictions for the hierarchical growth of dark matter 
    halos and galaxies (e.g. \citealt{Baugh1996, DeLucia2006}), but there are many 
    open questions regarding the star-formation history, mass assembly process, and 
    structural evolution of massive galaxies. 
    Massive galaxies are thought to grow according to a ``two-phase'' formation 
    scenario (e.g. \citealt{Oser2010, Oser2012}). 
    In this scenario, the progenitors of $z{\sim} 0$ massive early-type galaxies 
    (ETGs) undergo a rapid growth phase at $z{\sim} 2$ triggered either by disk 
    instabilities or gas-rich mergers (e.g. \citealt{Hopkins2008, Dekel2009}). 
    Observationally, the progenitors of ETGs are thought to correspond to the 
    population of massive quiescent galaxies at high redshift that have smaller 
    average effective radii ($R_{\mathrm{e}}$; e.g. \citealt{Trujillo2006, 
    vanDokkum2008, Cimatti2008}), slightly higher central velocity dispersion and 
    stellar mass density (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), and 
    more disk-like morphologies (e.g. \citealt{vanderWel2011}) than their local 
    descendants (e.g. \citealt{Bezanson2009, vanDokkum2010}) with similar stellar 
    mass.

    Following this initial epoch of early formation, feedback from stars and/or AGN 
    (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quench star formation in 
    massive galaxies. 
    A large fraction of these massive progenitors became quiescent at $z>1$ 
    (e.g. \citealt{Bezanson2009, Kriek2016}). 
    The second phase of their assembly is driven by non-dissipative processes such 
    as dry mergers with other galaxies (e.g. \citealt{Naab2006, Khochfar2006}). 
    To explain the observed increase of $R_{\mathrm{e}}$ (e.g. 
    \citealt{Newman2012, vdWel2014}) as well as the build-up of the outer stellar 
    halos of ETGs (e.g. \citealt{Szomoru2012, Patel2013}), the ``two-phase'' 
    scenario suggests that minor mergers should dominate the mass assembly during 
    the second phase (e.g. \citealt{Hilz2012, Hilz2013, Oogi2013, Bedorf2013, 
    Laporte2013}).
    Both numerical simulations (e.g. \citealt{Oser2010}) and 
    semi-analytic models (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the 
    mass fraction in the accreted component should increase with total stellar mass, 
    despite their technical differences (e.g. \citealt{Lackner2012, Cooper2013, 
    Qu2017}).
    For instance, recent result from the Illustris \footnote{
    \texttt{http://www.illustris-project.org/}} simulation 
    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) predicts that the fraction of  
    accreted stars increases significantly with total stellar mass at \logms{}$>11.0$, 
    and the accreted component starts to dominate the stellar mass budget 
    ($f_{\mathrm{accreted}}>0.5$) at \logms{}$>11.5$ (\citealt{RodriguezGomez2016}).
%% ------------------------------------------------------------------------------------ %%

    Given the success of this two-phase scenario in explaining trends like overall size 
    growth, it is time to confront their predictions with additional observations, 
    especially the detailed profiles of surface mass density and shape for low redshift 
    massive galaxies.  
    Early one-dimensional analysis of nearby massive ETGs suggest that the 
    single-\ser{} profile can describe their surface brightness (or surface mass 
    density) profiles reasonably well (e.g. \citealt{Kormendy2009}; except for the
    most central region), with the \ser{} index increasing with total luminosity 
    (e.g. \citealt{Graham2013}).
	However, the situation is in fact more complicated, with a suggestion from 
	\citet{Schombert2015} that there are actually two families of light profiles:
	the ones that follow single-\ser{} law well and the ones show significant 
	deviation.
	Two-dimensional analysis, meanwhile, finds that the stellar distributions 
    of massive ETGs are often better fit by multiple-component models 
    (e.g. \citealt{Huang2013a, Oh2017}). 
    \citet{Huang2013b} further suggests a connection between the multi-component 
    nature of massive galaxies and their two-phase assembly history. 
    To further confront the two-phase scenario requires very deep observations of 
    large samples of massive ETGs to correctly estimate their total stellar mass 
    (e.g. \citealt{Bernardi2013, DSouza2014}) and explore their assembly history via 
    their extended, accreted halos (e.g. \citealt{Capaccioli2015, Iodice2016, 
    Iodice2017}).
    Currently, such work is limited by the depth of imaging from large-area surveys 
    such as the Sloan Digital Sky Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}) or
    the small sample size of massive galaxies with deep images.

    In this paper, we take advantage of new high-quality (median 
    FWHM${\sim} 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
    limit $> 28.5$\sb) images from the Hyper Suprime-Cam (HSC) Subaru Strategic 
    Program \citep[SSP,][]{HSCDR1} to characterize the outer parts of massive galaxies 
    as a function of their properties. 
    The deep imaging depth and excellent seeing conditions of HSC images make them 
    perfect for mapping the \mstar{} distributions of massive galaxies out to very 
    large radii. 
    With the help of reliable spectroscopic and photometric redshift 
    (e.g. the ones for \redm{} clusters, \citealt{Rykoff2014}; \citealt{Rozo2015b}),
    we select a large sample (${\sim} 7000$) of massive central galaxies at 
    $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer. 
    In this paper, we use this sample to 
    (a) reliably measure individual surface mass density (\mden{}) profile of 
    massive galaxy out to 100 kpc, 
    (b) investigate the dependence of their outer stellar halos on total stellar 
    mass, and 
    (c) examine the implications for the stellar mass function (SMF) when the outer 
    halos of massive galaxies are accounted for.   
    In a second paper in this series, we will further look into the potential 
    environmental dependence of structures in massive ETGs (Huang\etal in prep.).

    This paper is organized as follows. 
    Section \ref{sec:data} presents our data and our sample selection. 
    Section \ref{sec:ellipse} describes our procedure for extracting 1-D surface 
    brightness profiles. 
    Section \ref{sec:mstar} describes how we estimate stellar mass. 
    Our main results are presented in Section \ref{sec:result} and discussed in 
    Section \ref{sec:discussion}. 
    Section \ref{sec:summary} presents our summary and conclusions.

    Magnitudes use the AB system (\citealt{Oke1983}), and are corrected for Galactic 
    extinction using calibrations from \citet{Schlafly11}.
    In this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_{\rm m}=0.3$, 
    and ${\Omega}_{\rm \Lambda}=0.7$.
    Stellar mass is noted \mstar{} and has been derived using a Chabrier Initial Mass 
    Function (IMF; \citealt{Chabrier2003}).

    $M_{\mathrm{halo}}$ denotes halo mass in general whereas $M_{\rm 200b}$ is 
    explicitly defined as $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
    \frac{4}{3}\pi r_{\rm 200b}^3$ where $r_{\rm 200b}$
    is the radius at which the mean interior density is equal to 200 times
    the mean matter density ($\bar{\rho}$).

@@

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_example}
        \caption{
            Left: example of the 1-D surface brightness and ellipticity profile 
            for a massive galaxy at $z=0.23$ in the $i$-band using \texttt{Ellipse}. 
            In this work, we always show the radial profile using a $R^{1/4}$ scaling 
            on the x-axis. 
            By using this scale, the de Vaucouleurs profile will appear as a straight 
            line on this figure. 
            We also plot the relative brightness profile of the PSF model normalized 
            at the central surface brightness of the galaxy to highlight the region 
            affected by seeing. 
            The grey shaded region highlights the region most affect by seeing 
            ($r<3$ kpc).
            On the top panel, the dash line shows the ellipticity used for the final 
            isophote. 
            Right: the three color image of this galaxy with isophotes 
            extracted by \texttt{Ellipse}. 
            The thick dotted line highlights the isophote with 
            $\mu_{i}{\sim} 28.5$~\sb.
            }
        \label{fig:ellipse}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    The Subaru Strategic Program (SSP, \citealt{HSC_SSP, HSC_DR1}) makes use of the 
    new prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 
    8.2-m Subaru telescope at Mauna Kea. 
    The ambitious multi-layer HSC survey takes advantage of the large field of 
    view (FoV;~1.5 deg in diameter) of this camera and will cover $>1000$ deg$^2$ 
    of sky in 5 broad bands ($grizy$) to a limiting depth of $r {\sim} 26$ mag 
    in the \texttt{WIDE} layer. 
    This work is based on the internal data release \texttt{S15B}, which covers 
    ${\sim} 100$ deg$^2$ in all 5-band to full \texttt{WIDE} depth.  
    The regions covered by this release overlap with a number of spectroscopic surveys 
    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).

    The HSC \texttt{WIDE} survey is about $3.0$-$4.0$ magnitudes deeper in the 
    $i$-band surface brightness limit than SDSS. 
    Combined with the excellent imaging resolution (the median $i$-band seeing is 
    0.6\asec) and the wide area, the HSC survey represents a tremendous dataset to 
    perform large statistical study of the surface brightness profiles of massive
    galaxies out to their very outskirts.     
    Fig~\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
    for three low redshift ETGs, and shows that HSC survey data are well suited for 
    mapping the stellar distribution of massive galaxies out to large radii.

	HSC $i$-band images typically have the best seeing compared to other bands because 
	of strict requirements driven by weak lensing science. 
    We will therefore use the $i$-band images to measure the stellar distributions of 
    massive galaxies.

%% ------------------------------------------------------------------------------------ %% 
\subsection{HSC Data Processing}
    \label{sec:pipeline}

    The full details of the HSC data processing can be found in \citet{Bosch2017}
    and are briefly summarized here. 
    The HSC SSP data are processed with \texttt{hscPipe 4.0.2}, a derivative of the 
    Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
    \citealt{Axelrod2010}), modified for HSC. 
    \texttt{hscPipe} first performs a number of tasks at the single exposure level 
    (bias subtraction, flat fielding, background modeling, object detection and 
    measurements). 
    Astrometric and photometric calibrations are performed at the single exposure 
    level. 
    \texttt{hscPipe} then warps different exposures on to a common World Coordinate 
    System (WCS) and combines them into coadded images. 
    At this stage, \texttt{hscPipe} updates the images with a better astrometric and 
    photometric calibration using stars that are common among exposures.

>>>>

% Version 0; preprint format; Written by SH
% Version 1; emulateapj format; Edited by SH and AL
% Version 2; emulateapj format; Edited by SH and AL
% Version 3; emulateapj format; Edited AL
% Version 4; emulateapj format; Edited SH
% Version 5; MNRAS format; Edited SH
% Version 6; MNRAS format; Paper I edited by JG
% Version 7; MNRAS format; Edited by SH
% Version 10; MNRAS format; Edited by AL and JG
% Version 11; MNRAS format; Edited by SH
% Version 12; MNRAS format; Edited by SH
% Version 13; MNRAS format; Edited by KB
% Version 14; MNRAS format; Edited by SH, response to the referee report
% Version 15; MNRAS format; Edited by Susan Foster
% Version 16; MNRAS format; Edited by SH, response the the referee report

\documentclass[fleqn,usenatbib]{mnras}

@@

\def\m2l{{$M_{\star}/L$}}
\def\s2n{{$\mathrm{S}/\mathrm{N}$}}
\def\mden{{$\mu_{\star}$}}

% Commenting:
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
\newcommand{\addref}{{\textcolor{red}{REF}}}
\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
\newcommand{\song}[1]{\textcolor{cyan}{\textbf{#1}}}
\newcommand{\susan}[1]{\textcolor{Bittersweet}{\textbf{#1}}}
\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
\newcommand{\jenny}[1]{\textcolor{Bittersweet}{\textbf{[Jenny: #1]}}}
\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
\newcommand{\rachel}[1]{\textcolor{cyan}{\textbf{[Rachel: #1]}}}
\newcommand{\update}[1]{\textcolor{PineGreen}{#1}}
%\newcommand{\update}[1]{#1}

@@

%% ------------------------------------------------------------------------------------ %% 
\title[Mass Dependent Stellar Haloes in Massive Galaxies]{Individual Stellar Haloes of 
	   Massive Galaxies Measured to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam}

\author[S. Huang et al.]{
        Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
        Alexie Leauthaud,$^{2,1}$
        Jenny E. Greene,$^{4}$
        Kevin Bundy,$^{3,1}$
        \newauthor
        Yen-Ting Lin,$^{5}$
        Masayuki Tanaka,$^{5}$
        Satoshi Miyazaki,$^{5,7}$
        \newauthor
        Yutaka Komiyama$^{5,7}$
        \\
        $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
              the University of Tokyo, Kashiwa 277--8583, Japan\\
        $^{2}$Department of Astronomy and Astrophysics, University of California 
              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
        $^{3}$UCO/Lick Observatory, University of California, Santa Cruz,
              1156 High Street, Santa Cruz, CA 95064, USA\\
        $^{4}$Department of Astrophysical Sciences, Peyton Hall,
              Princeton University, Princeton, NJ 08540, USA \\
        $^{5}$National Astronomical Observatory of Japan, 2--21--1 Osawa, Mitaka, 
              Tokyo 181--8588, Japan\\
        $^{6}$Academia Sinica Institute of Astronomy and Astrophysics, 
              P.O. Box 23--141, Taipei 10617, Taiwan\\
        $^{7}$SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
              Tokyo, 181--8588, Japan
        }   
%% ------------------------------------------------------------------------------------ %% 
\date{Accepted XXX. Received YYY; in original form ZZZ}        
\pubyear{2017}

@@

    Massive galaxies display extended light profiles that can reach several 
    hundreds of kiloparsecs. 
    We use data from the Hyper Suprime-Cam (HSC) survey that is simultaneously wide 
    (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in $i$-band) to study the stellar 
    haloes of a sample of ${\sim}7000$ massive galaxies at $z{\sim}0.4$. 
    The depth of the HSC data enables us to measure surface mass density profiles 
    to 100 kpc for individual galaxies without stacking. 
    As in previous work, we find that more massive galaxies exhibit more extended outer 
    profiles than smaller galaxies.
    When this extended light is not properly accounted for (because of shallow imaging 
    and/or inadequate profile modeling), the derived stellar mass function can be 
    significantly underestimated at the high mass end.  
    Across our sample, the ellipticity of outer light profile increases substantially 
    with radius.  
    We show for the first time that these ellipticity gradients steepen dramatically as 
    a function of galaxy mass, but we detect no mass-dependence in outer color gradients. 
    Our results support the two-phase formation scenario for massive galaxies in which 
    outer envelopes are built up at a later time from a series of merging events. 
    We provide surface mass density profiles in a convenient tabulated format 
    to facilitate comparisons with predictions from numerical simulations of 
    galaxy formation.

@@

    Massive early-type galaxies (ETGs) are predicted to assemble according to a 
    `two-phase' formation scenario 
    (e.g. \citealt{Oser2010, Oser2012}): a rapid growth phase at high-redshift that 
    is dominated by intense dissipative \textit{in situ} star formation (e.g.
    \citealt{Hopkins2008, Dekel2009}), and a second phase that 
    is driven by non-dissipative processes such as dry mergers 
    (e.g. \citealt{Naab2006, Khochfar2006}), with an important role played by 
    minor mergers 
    (e.g. \citealt{Hilz2012, Hilz2013, Oogi2013, Bedorf2013, Laporte2013}).
    Both numerical simulations (e.g. \citealt{Oser2010}) and semi-analytic models 
    (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the fraction of stellar 
    mass accreted in the second phase (the \textit{ex situ} component) should increase 
    with total galaxy stellar mass (e.g. \citealt{Lackner2012, Cooper2013, Qu2017}).
    For instance, recent results from the 
    Illustris\footnote{\texttt{http://www.illustris-project.org/}} simulation 
    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) predict that the fraction of  
    accreted stars increases significantly with galaxy mass, reaching
    $f_{\mathrm{accreted}}>0.5$ at \logms{}$>11.5$ 
    (\citealt{RodriguezGomez2016})\footnote{The Illustris simulation
    does not reproduce the observed stellar mass function at the high mass end.}. 
%% ------------------------------------------------------------------------------------ %%

    Given the success of the `two-phase' scenario in explaining the properties of 
    high-$z$ massive quiescent galaxies (e.g. \citealt{vanDokkum2010, vanderWel2011,
    vandeSande2011, Belli2014}) and the dramatic increase of their effective radii 
    ($R_{\mathrm{e}}$; e.g. \citealt{Newman2012, vdWel2014}), it is time to confront 
    this model with additional observations, in particular, the detailed surface 
    mass density profiles of low-redshift massive galaxies. 
    Early studies based on one-dimensional light profiles found that the surface 
    mass density profiles of nearby ETGs are well described by single-\ser{} profiles 
    (e.g. \citealt{Kormendy2009}; except for the most central regions) and that the 
    \ser{} index increases with total luminosity 
    (e.g. \citealt{Graham2013}). 
    A more recent study of the surface brightness profiles of ETGs 
    revealed that ETGs belong to two families: 
    those that follow single-\ser{} law, versus those that significantly deviate from 
    the single-\ser{} profile \citep{Schombert2015}.  
    Two-dimensional analyses have also found that the stellar distributions of massive 
    ETGs are often better described by multiple-component models 
    (e.g. \citealt{Huang2013a, Oh2017}).  
    \citet{Huang2013b}, further suggesting a connection between the multi-component 
    nature of massive galaxies and their two-phase assembly histories.

    To further confront the two-phase scenario requires very deep observations of 
    large samples of massive ETGs to correctly estimate their total stellar masses
    (e.g. \citealt{Bernardi2013, DSouza2014}), as well as to quantify the amplitude and 
    scatter among outer envelopes (e.g. \citealt{Capaccioli2015, Iodice2016, 
    Iodice2017}).
    To date, large samples of massive galaxies with deep imaging have been lacking. 
    Even in the nearby universe, it is not trivial to map the low surface
    brightness outskirts of massive galaxies (e.g., 
    \citealt{Capaccioli2015, Iodice2016, Iodice2017, Spavone2017, Mihos2017}). 
    Some of these measurements are based on image stacking methods (e.g. 
    \citealt{Tal2011, dSouza2015}). 
    The number of very massive galaxies is also very limited in the local universe.
    For example, according to the \texttt{MASSIVE} survey (\citealt{Ma2014}), there
    are only $\sim 60$-70 massive galaxies with \logms$> 11.6$ (based on K-band 
    luminosity) within 108 Mpc.

    In addition to mass density profiles, the radial profile of ellipticity also 
    contains information about the 3-D geometry (e.g. \citealt{Tremblay1995, 
    Tremblay1996, Chang2013, RodriguezPadilla2013, Mitsuda2017}) and kinematics 
    (e.g. \citealt{Cappellari2012, Weijmans2014}) of stars in massive galaxies.
    If the stellar haloes of massive galaxies are indeed dominated by accreted 
    stars, their ellipticities could be systematically different with the inner 
    regions and may contain clues about the assembly history of massive galaxies 
    (e.g. average time since last merger, average merger mass ratio).
    These issues have not been fully explored in both simulation and observation.
    Certain simulation predicts that a more massive ETG should have rounder shape
    (e.g. \citealt{Wu2014}), while others generate massive galaxies with very 
    elongated haloes (e.g. \citealt{Li2017}).  
    On the observational side, constraints are only available from a few works 
    that use either an image stacking method (e.g. \citealt{Tal2011, dSouza2015}) 
    or a small sample of nearby galaxies (e.g. \citealt{Spavone2017}).

    In this paper, we take advantage of the high-quality deep images from the 
    Hyper Suprime-Cam (HSC) Subaru Strategic Program (SSP) \citep[SSP,][]{HSC-DR1} 
    (see \S~\ref{ssec:hsc} for details) to characterize  the light profiles of 
    massive galaxies out to 100 kpc. 
    We select a large sample (${\sim} 7000$) of massive central galaxies 
    at $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer. 
    %\susan{Note that MNRAS requirement is to use British spelling; however, 
    %they also prefer the -ize variant of word such as recognize, criticize, 
    %minimize, emphasize, organize, ionize, polarize, parametrize (etc.).}

    We use this sample to 
    (1) reliably estimate individual surface mass density (\mden{}) profiles of 
    massive galaxies out to 100 kpc, 
    (2) investigate the dependence of their outer stellar haloes on total stellar 
    mass, and 
    (3) examine the implications in terms of evaluating the high mass end of the 
    galaxy stellar mass function (SMF). 
    In a second paper in this series (Huang \etal in prep.), we will investigate 
    the environmental (dark matter halo mass) dependence of the sizes of massive 
    ETGs (Huang\etal in prep.).

    This paper is organized as follows. 
    \S~\ref{sec:data} presents our data and initial sample selection. 
    \S~\ref{sec:ellipse} describes our procedure for extracting 1-D surface 
    brightness profiles. 
    \S~\ref{sec:mstar} describes how we estimate stellar mass.
    \S~\ref{sec:final} summarizes the final sample selection procedure. 
    Our main results are presented in \S~\ref{sec:result} and discussed in 
    \S~\ref{sec:discussion}. 
    \S~\ref{sec:summary} presents our summary and conclusions.

    Magnitudes use the AB system (\citealt{Oke1983}), and are corrected for galactic 
    extinction using calibrations from \citet{Schlafly11}.
    In this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_{\rm m}=0.3$, 
    and ${\Omega}_{\rm \Lambda}=0.7$.
    Stellar mass is denoted \mstar{} and has been derived using a Chabrier Initial Mass 
    Function (IMF; \citealt{Chabrier2003}).

    Halo mass is defined as 
    $M_{\rm 200b}\equiv M(<r_{\rm 200b})=200\bar{\rho} 
    \frac{4}{3}\pi r_{\rm 200b}^3$ where $r_{\rm 200b}$
    is the radius at which the mean interior density is equal to 200 times
    the mean matter density ($\bar{\rho}$).

    We emphasize that in this work we do not attempt to disentangle the 
    galaxy light from any `intra-cluster' light component (ICL; e.g. 
    \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}). 
    Although the rising stellar velocity dispersion in the outskirts of massive 
    brightest cluster galaxy (BCG)
    hints at a kinematically separated intra--cluster light (ICL) component (e.g. 
    \citealt{Dressler1979, Carter1999, Kelson2002, Bender2015, Longobardi2015}),
    it is extremely difficult to reliably isolate it photometrically.
    Moreover, both the stellar halo of the main galaxy and the ICL component carry 
    important information regarding the assembly history of the central galaxy and its 
    dark matter halo. 
    Therefore, we adopt the view that the light of the main galaxy and the 
    ICL component trace different scales of a single, smooth, and continuous 
    distribution.

@@

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_example}
        \caption{
            \textbf{Left}: Example of the 1-D surface brightness and ellipticity 
            profile of a massive galaxy at $z=0.23$ in the $i$-band extracted using 
            \texttt{Ellipse}. 
            In this work, we always show the radial profile using a $R^{1/4}$ scaling 
            on the x-axis.
            By using this scale, the de Vaucouleurs profile will appear as a straight 
            line on this figure.  
            We also plot the relative brightness profile of the PSF model normalized 
            at the central surface brightness of the galaxy to highlight the region 
            most strongly affected by seeing.
            The grey shading highlights the region ($r<6$ kpc) that is equivalent 
            to twice the size of the half-width of a 1\asec{} seeing at $z\sim 0.5$.
            Because it is a very conservative estimate of the region, we cannot reliably 
            extract a 1-D profile due to the smearing effect of seeing.
            On the top panel, the dashed line shows the mean ellipticity used for the 
            final isophote. 
            \textbf{Right}: The 3-colour image of this galaxy with isophotes 
            extracted by \texttt{Ellipse}. 
            The thick dotted line highlights the isophote with 
            $\mu_{i}{\sim} 28.5$~\sb.
            }
        \label{fig:ellipse}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    The Subaru Strategic Program (SSP, \citealt{HSC-SSP, HSC-DR1}) makes use of the 
    new prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}, 
    Miyazaki in~prep.), on the 
    8.2-m Subaru telescope at Mauna Kea. 
    The ambitious multi-layer HSC survey takes advantage of the large field of 
    view (FoV;~1.5 deg in diameter) of this camera and will cover $>1000$ deg$^2$ 
    of sky in five broad bands ($grizy$) to a limiting depth of $r {\sim} 26$ mag 
    in the \texttt{WIDE} layer. 
    This work is based on the internal data release \texttt{S15B}, which covers 
    ${\sim} 110$ deg$^2$ in all five bands to full \texttt{WIDE} depth.  
    The regions covered by this release overlap with a number of spectroscopic 
    surveys 
    [e.g.\ Sloan Digital Sky Survey (SDSS)/Baryon Oscillation Spectroscopic Survey 
    (BOSS): \citealt{Eisenstein2011}, \citealt{SDSS-DR12}; 
    Galaxy And Mass Assembly (GAMA): \citealt{Driver2011}, \citealt{Liske2015}].
    \texttt{S15B} release has similar sky coverage with the Public Data Release 1
    (Please see Table 3 in \citealt{HSC-DR1} for detailed comparison).

    The HSC \texttt{WIDE} survey is about $3.0$-$4.0$ magnitudes deeper in terms of 
    the $i$-band surface brightness limit than SDSS. 
    Combined with the excellent imaging resolution (the median $i$-band seeing is 
    0.6\asec) and the wide area, the HSC survey represents an ideal dataset to perform 
    statistical studies of the surface brightness profiles of massive galaxies out to 
    their distant outskirts.  
    Fig~\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
    for three low-redshift ETGs, and shows that HSC survey data are well suited for 
    mapping the stellar distribution of massive galaxies out to large radii.

	HSC $i$-band images typically have the best seeing compared to other bands because 
	of strict requirements driven by weak lensing science. 
    We therefore use $i$-band images to measure the stellar distributions of 
    massive galaxies.

%% ------------------------------------------------------------------------------------ %% 
\subsection{HSC data processing} 
    \label{sec:pipeline}

    The full details of the HSC data processing can be found in \citet{HSC-PIPE}
    and are briefly summarized here. 
    The HSC SSP data are processed with \texttt{hscPipe 4.0.2}, a derivative of the 
    Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
    \citealt{Axelrod2010}), modified for HSC. 
    \texttt{hscPipe} first performs a number of tasks at the single exposure level 
    (bias subtraction, flat fielding, background modelling, object detection and 
    measurements). 
    Astrometric and photometric calibrations are performed at the single exposure 
    level. 
    \texttt{hscPipe} then warps different exposures on to a common World Coordinate 
    System (WCS) and combines them into coadded images. 
    At this stage, \texttt{hscPipe} updates the images with a better astrometric and 
    photometric calibration using stars that are common among exposures.
